\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[a4paper, margin=1.2in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}

\usepackage{hyperref}

\title{Exploring Aliasing and the Sampling Theorem} %\\\large\textit{Approximation Part 2 Assignment}}
\author{Margherita Tonon}
\date{April 2025}

\begin{document}

\maketitle

\section{Introduction}
In signal processing, \dots %introduction sentence, context, motivation

An analog signal refers to a signal that varies continuously over time. 
The complexity of analog signal processing, their susceptibility to noise and signal degradation over time, as well as their limited reproductibility and scalability makes them inconvenient to work with in practice. 
Therefore, digital signals are used -- signals that vary discretely over time and can take only a finite number of distinct values.
%mention advantages of digital signals?

Sampling refers to the process of converting an analog signal into a digital signal. If we let $x(t)$ be a continuous time signal, the sampled signal $x[n]$ is defined as
\begin{center}
    \begin{math}
        x[n] = x(nT_s)
    \end{math}  
\end{center}
where $n$ represents discrete time sampling points and $T_s$ represents the sampling period, such that the sampling frequency $f_s = \frac{1}{T_s}$.

Sampling can also be represented as 
\begin{center}
    \begin{math}
        x_s(t) = x(t) \sum_{-\infty}^{\infty} \delta (t-nT_s)
    \end{math}  
\end{center}
where $x_s(t)$ is the sampled points, and $\delta$ is the dirac delta distribution, taking value 1 if $t=nT_s$ and 0 otherwise.
Therefore, it is clear that when $t=nT_s$, $x_s(t) = x(t)$; otherwise $x_s(t) = 0$. 

In practice, sampling allows us to discretize a continuous input, facilitating the handling of signals. After sampling is done, it is natural that the signal must be reconstructed in order to recover the original (time continuous) signal.
However, recovery is not always perfect -- the Shannon-Nyquist condition must be met.
%something along the lines of: the key issue is what must the sampling frequency be in order for a signal to be perfectly reconstructed and recovered?

The Shannon-Nyquist theorem states that a signal can be perfectly reconstructed if the sampling frequency is greater than two times the maximum frequency of the continuous signal:
\begin{center}
    \begin{math}
        f_s > 2B
    \end{math}  
\end{center}
where $B$ is the maximum frequency in Hertz.
For example, if we consider a sine wave with frequency 5 Hertz, $\sin(2\pi \cdot 5 \cdot t)$, once sampled it can be perfectly reconstructed if the sampling frequency is greater than 10.
%TODO: need to check what the relationship between B and the max continuous frequency is

%do i explain quantization here?

In the time domain, a sampled signal looks like discrete spikes (Figure 1). To visualize what this looks like in the frequency domain, we make use of the Convolution Theorem.
The Convolution Theorem states that 


%some context into the problem, theory
%overview of what sampling is, why its used!! important to say why sampling
%what happens when we sample?
%the problem of reconstruction and the need for sufficiently high sampling frequencies

\section{Implementation}
%explanation of code, and I think here you would explain things like the theory behind the sinc function


\section{Discussion}
%results of code
%different initial frequencies, different sampling frequencies based on shannon nyquist thm

\section{Conclusion}

\end{document}
